Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-22 paper.tex
Section3 minor typos

\noindent It is estimated that almost half a billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives. Modern improvements in mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem. The work presented here is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone. The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017,bellotto2013}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}. Schematically, the actuators used in a typical control loop, shown in Figure~\ref{fig:control-loop}, are replaced by a human. %This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.

@@

In this case, the reference signal, $r$, is the object the user wishes to capture with the smartphone's camera. The goal of the control block, $K$, is to generate human interpretable instructions, $u$, to guide the user towards the target object. The process to be controlled involves a human, $H$, who interprets the instruction and executes a physical action, $u^*$, to actually manipulates the smartphone's camera, $P$. A new observation, $y$, with the latter is then fed back to the loop and the error signal, $e$, is updated accordingly.

Here we focus in particular on the implementation of the control module $K$. Two important points are considered in the design of the controller. Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places, unknown a priori. Secondly, the controller must be robust enough to handle incorrect interpretations by the human of the instructions $u$. This risk can be mitigated by the use of clear and simple instructions that help $u^*$ follow as close as possible $u$. The implementation of this controller is discussed in detailed next.

>>>>

\noindent It is estimated that almost half a billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives. Modern improvements in mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem. The work presented here is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone. The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017,bellotto2013}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of a user holding the smartphone, as pictured in Figure~\ref{fig:system-use}. Schematically, the actuators used in a typical control loop, shown in Figure~\ref{fig:control-loop}, are replaced by a human. %This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.

@@

In this case, the reference signal, $r$, is the object the user wishes to capture with the smartphone's camera. The goal of the control block, $K$, is to generate human interpretable instructions, $u$, to guide the user towards the target object. The process to be controlled involves a human, $H$, who interprets the instruction and executes a physical action, $u^*$, to actually manipulate the smartphone's camera, $P$. A new observation, $y$, with the latter is then fed back to the loop and the error signal, $e$, is updated accordingly.

Here we focus in particular on the implementation of the control module $K$. Two important points are considered in the design of the controller. Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places, with unknown a priori. Secondly, the controller must be robust enough to handle incorrect interpretations by the human of the instructions $u$. This risk can be mitigated by the use of clear and simple instructions that helps $u^*$ to track $u$ as close as possible. The implementation of this controller is discussed in detailed next.
